Borel regularity for ODEs and Thimble Integrals

### 2024-01-25 exp-resurgence.tex
Revise Section 3

\textcolor{orange}{[State theorem: differentiation commutes with $\aexp^\theta$ under certain circumstances. See Erdelyi's {\em Asymptotic Expansions}, \S 1.6]}

@@

Let $b\in B$ be an ordinary point, and let $\zeta_b$ be a coordinate on $B$ so that $\zeta = b + \zeta_b$, then the Laplace transform $\laplace_{\zeta_b,0}$ is defined on $T^*_{b}B$ and it's compatible with $\laplace_{\zeta,b}$.  

@@

    e^{-b z} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.

@@

 \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{zb}\,\mathcal{O}_{T^*B}(H)\\

@@

commutes, where $H$ on the left-hand-side is the right half plane $\Re z>0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).

@@

    The result follws from a simple calculation:

@@

\color{orange}
\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
\color{black}
On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate. This formal inverse is called the {\em Borel transform}. To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow{u}{\laplace_{\zeta, 0}}
\end{tikzcd}
\end{center}
and it extends to formal power series by linearity 
\begin{align*}
\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
\end{align*}

\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}

@@

If we'd expanded $\varphi$ as a Taylor series ${\varphi}_b$ in the translated coordinate $\zeta_b$ from above, we could have taken the Laplace transform $\laplace_{\zeta_b,0}$ instead, giving a power series in $z^{-1}$ that represents a function on $T^*_{\zeta = b}B$. Using the Borel transform with respect to $\zeta_b$, defined like the formal inverse of $\laplace_{\zeta_b,0}$
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_b}} \\ \{1, \zeta_b, \zeta_b^2, \zeta_b^3, \ldots\} \arrow{u}{\laplace_{\zeta_b, 0}}
\end{tikzcd}
\end{center}
and extended to formal power series by linearity $\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_b \rrbracket$,
%\begin{align*}
%\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C %\llbracket \zeta_b \rrbracket \\
%\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta_b^n}{n!},
%\end{align*}
%%\begin{align*}
 %%    \borel_{\zeta_b}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_b \rrbracket  \\
  %%   z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
 %%\end{align*}
we could again recover ${\varphi}_b$.

@@

\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_\alpha"']      &  & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha,0}"]\arrow{uu}{\laplace_{\zeta,\alpha}}

@@

commutes, where $\mathsf{T}_\alpha$ denote the traslation by $\alpha$. Notice that the functions on the varible $z$ are meant to be on the fiber $T^*_{\zeta=0}B$. 

@@

@@

So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$. These formal series are the so-called $1$-Gevrey series:

@@

\begin{notation*}
We want to distinguish between formal series and holomorphic functions, as well as between the spatial domain (Borel plane) and the frequency domain ($z$-plane). Therefore we adopt the following notation:
\begin{itemize}
\item $\Phi$: upper-case letters are holomorphic functions on the frequency domain;
\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
\item $\phi$: lower-case letters are holomorphic functions on the frequency domain. Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane. As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$; 
\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
\end{itemize}
\end{notation*}

\begin{lemma}
Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$. Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions. 
\end{lemma}

In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}. In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhisms.

\subsubsection{Action on power series with fractional exponents}
The definition of the Borel transform can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
\begin{align*}
\borel_\zeta(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
\end{align*}
and then extending by linearity.

\subsubsection{Action on fractional derivatives and fractional integrals}
For applications is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.

Recall that for $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$: 
%
\begin{equation*}
    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi(\zeta_\alpha+\alpha)\, d\zeta_\alpha.
\end{equation*}}

@@

\begin{lemma}\label{L-int-op}
    The following identities hols true:

>>>>

\textcolor{orange}{[State theorem: differentiation commutes with $\aexp^\theta$ under certain circumstances. See Erdelyi's {\em Asymptotic Expansions}, \S 1.6. For basic facts about uniform asymptoticity, see \S 5.7.2 of Mitschi and Sauzin. Theorem~5.20 and its rephrasing say that the Laplace transform of a function is uniformly asymptotic to the formal Laplace transform of the function's Taylor series.]}

@@

Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$. Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.  

@@

    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.

@@

 \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{bz}\,\mathcal{O}_{T^*B}(H)\\

@@

commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).

@@

With a change of variable in the integral that defines the Laplace transform, we see that

@@

\color{orange}
\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
\color{black}
On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate. This formal inverse is called the {\em Borel transform}. To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \left\{1, \zeta, \frac{1}{2!} \zeta^2, \frac{1}{3!} \zeta^3, \ldots\right\} \arrow{u}{\laplace_{\zeta, 0}}
\end{tikzcd}
\end{center}
and it extends to formal power series by linearity 
\begin{align*}
\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
\end{align*}
\begin{remark}
The definition of the Borel transform can be easily extended to fractional power of $z$: indeed notice that   
\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
for every $\sigma\in\R\setminus\Z_{\leq 0}$. Thus 
\begin{align*}
\borel_\zeta(z^{-\sigma-1})\defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)} 
\end{align*}
and then extended by linearity to $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$. 
\end{remark}
%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}

@@

If we'd expanded $\varphi$ as a Taylor series ${\varphi}_b$ in the translated coordinate $\zeta_b$ from above, we could have taken the Laplace transform $\laplace_{\zeta_b,0}$ instead, giving a power series in $z^{-1}$ that represents a function on $T^*_{\zeta = b}B$. Using the Borel transform with respect to $\zeta_b$, defined like the formal inverse of $\laplace_{\zeta_b,0}$
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_b}} \\ \{1, \zeta_b, \frac{1}{2!} \zeta_b^2, \frac{1}{3!} \zeta_b^3, \ldots\} \arrow{u}{\laplace_{\zeta_b, 0}}
\end{tikzcd}
\end{center}
and extended to formal power series by linearity $\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_b \rrbracket$,
%\begin{align*}
%\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C %\llbracket \zeta_b \rrbracket \\
%\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta_b^n}{n!},
%\end{align*}
%%\begin{align*}
 %%    \borel_{\zeta_b}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_b \rrbracket  \\
  %%   z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
 %%\end{align*}
we could again recover ${\varphi}_b$.

@@

\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"']      &  & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha,0}"]\arrow{uu}{\laplace_{\zeta,\alpha}}

@@

commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$. Notice that the functions of the varible $z$ are meant to be on the fiber $T^*_{\zeta=0}B$. 

@@

\subsubsection{Action on translations in the frequency domain}
Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can deduce how $\borel_\zeta$ acts on translations in the frequency domain, namely we can show that for $\varphi=\sum_{n=0}^\infty a_n z^{-n-1}$
\[\borel_\zeta \mathsf{T}_{-c}^* \varphi=e^{-c\zeta }\borel_\zeta\varphi.\]
Indeed, the following diagram
\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{dd}{\borel_\zeta}\arrow[rr,"\mathsf{T}_{-c}^*"]& &  \{(z+c)^{-1}, (z+c)^{-2}, (z+c)^{-3}, (z+c)^{-4}, \ldots \} \arrow{dd}{\borel_\zeta}    \\
\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "e^{-c\zeta}"'] \arrow{uu}{\laplace_{\zeta,0}}     &  & e^{-c\zeta}\{1, \zeta, \zeta^2, \zeta^3, \ldots\}\arrow{uu}{\laplace_{\zeta,0}}
commutes, where the functions of the variable $z$ belong to the fiber $T^*_{\zeta=0}B$. If $z$ is a function on the fiber over $\zeta=b$, then it's enough to replace $\borel_\zeta$ with $\borel_{\zeta_b}$ and to use  $\laplace_{\zeta_b,0}$ as the inverse. 
%\color{orange}
%\subsubsection{Action on power series with fractional exponents}

@@

The space of formal power series $\C\llbracket z^{-1}\rrbracket$ is a $\C$-algebra with unit $1$, thus by definition the Borel transform is a $\C$-algebra homomorphisms between $\C\llbracket z^{-1}\rrbracket$ and $\C\delta +\C\llbracket\zeta\rrbracket$, where $\delta:=\borel_\zeta (1)$ denotes the formal unit on $\C\llbracket\zeta\rrbracket$.

In fact, since $\borel_\zeta$ is deifned as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by linearity. As a result, we find that the \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\] 
is a $\C$-algebra isomorphism whose inverse is the formal Laplace transform.

However, as we discussed in Section~\ref{sec:reg-decay}, the Laplace transform $\laplace_{\zeta,0}$ is naturally defined on the space of integrable, holomorphic functions, namely $\singexpalg{\sigma}(\Omega)\subset \zeta^{\sigma}\C\lbrace\zeta\rbrace$ for $\sigma>-1$, hence we might expect it extends to a $\C$-algebra homomorphism from $\singexpalg{\sigma}(\Omega)$ to $\mathcal{O}(H)$. Indeed, that's the case, but it requires to introduce the convolution product on the space of analytic functions $\zeta^{\sigma-1}\C\lbrace\zeta\rbrace$. We'll discuss it in Section~\ref{convolution}.

Consequently, also at the formal level we can restric to a subalgebra of $\C\llbracket z^{-1}\rrbracket$ whose image under $\borel_\zeta$ lies in $\C\lbrace\zeta\rbrace$. This subalgebra is the so called space of $1$-Gevrey series $\C\llbracket z^{-1}\rrbracket_1\subset\C\llbracket z^{-1}\rrbracket$ and $\borel_\zeta\colon \C\llbracket z^{-1}\rrbracket_1\to\C\delta+\C\lbrace\zeta\rbrace$ is a $\C$-algebra homomorphism (see Section~\ref{sec:Borel-gevrey}).

Finally in Section~\ref{sec:frac-diff-laplace}, we'll consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives both in the frequency and the position domain, and fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain. %We'll see that the Borel transform and formal Laplace transform commutes with the action of derivatives and moltiplication. %from the space of Puiseux series in the frequency domain to  $\C\llbracket z^{-1}\rrbracket$

We end this paragraph introducing the notation we'll be using in the following. 
\begin{notation*}
We want to distinguish between formal series and holomorphic functions, as well as between the spatial domain (Borel plane) and the frequency domain ($z$-plane). Therefore we adopt the following notation:
\begin{itemize}
\item $\Phi$: upper-case letters are holomorphic functions on the frequency domain;
\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
\item $\phi$: lower-case letters are holomorphic functions on the frequency domain. Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane. As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel_\zeta \tilde{\Phi}=:\tilde{\phi}$; 
\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
\end{itemize}
\end{notation*}  
%between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with th
%In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. \textcolor{orange}{[Why not say this more generally, with $\C\llbracket z^{-1} \rrbracket$ and $\C\llbracket\zeta\rrbracket$?]} The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}. \textcolor{orange}{[This seems a little weird to me, since we define the Borel transform as a formal inverse to the Laplace transform. Wouldn't it be easier to define the formal Laplace transform as a formal version of the Laplace transform, and then define the Borel transform as its inverse?]} In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhism.

\subsubsection{The convolution product}\label{convolution}
%
Let $\series{\phi},\series{\psi}\in\C\lbrace\zeta\rbrace$ be two convergent formal series in a neighbourhood of $\zeta=0$, and let $\hat{\phi}$ and $\hat{\psi}$ be respectively their sum in a common region of convergence, say $|\zeta|<R$. Then the convolution product $\hat{\phi}\ast\hat{\phi}$ is defined as
\begin{equation}\label{eq:convolution}
    \hat{\phi}\ast\hat{\psi}:=\int_0^{\zeta}\hat{\phi}(\zeta-\zeta')\hat{\psi}(\zeta')\, d\zeta'
\end{equation}
and it admits a convergent power series expansion for $|\zeta|<R$ (see \cite[Lemma 5.14]{diverg-resurg-i}).

In addition, we can relax the assumption on $\series{\phi},\series{\psi}$ by allowing integrable singularties at $\zeta=0$, namely  $\series{\phi}\in\zeta^{\sigma}\C\lbrace\zeta\rbrace$ and $\series{\psi}\in\zeta^{\tau}\C\lbrace\zeta\rbrace$ with $\sigma,\tau>-1$. In this case, $\hat{\phi}$ and $\hat{\psi}$ will be respectively the sum of the series $\series{\phi}$ and $\series{\psi}$ in an open domain $\Omega\cap \lbrace |\zeta|<R\rbrace$ (that may not contain $\zeta=0$). In fact, this leads to the definition of the convolution product for functions in $\singexp{\sigma}{\Lambda}(\Omega)$: 
\begin{lemma}
    Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega)$ for $\sigma>-1$, then $\phi\ast\psi\in\singexp{\sigma}{\Lambda}(\Omega)$.
\end{lemma}
\begin{verify}
\begin{proof}
    \begin{align*}
        | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
        &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
        &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
        &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
    \end{align*}
\end{proof}
\end{verify}
In addition, we can show that $\laplace_{\zeta,0}$ is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on the right-half-plane $\Re z>0$. 
\begin{prop}
    Let $\sigma>-1$ and $\Lambda>0$. The Laplace transform $\laplace_{\zeta,0}$ is $\C$-algebra homomorphism from $(\singexp{\sigma}{\Lambda}(\Omega),\ast)$ to to the space of holomorphic functions on the right-half-plane $\Re z>0$ with the standard multiplication of functions. 
\end{prop}
\begin{proof}
It is enough to show that
\[\laplace_{\zeta,0}\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}\big[{\phi}\big]\laplace_{\zeta,0}\big[{\psi}\big],\]
which indeed follows from simple integral computations (see for instance ~\cite[Theorem 2.39]{laplace-tfm}). 
\end{proof}
\begin{remark}
    it is possible to define an inverse Laplace transform, so that $\laplace_{\zeta,0}$ becomes an algebra isomorphisms. However we'll refer to \textcolor{magenta}{[standard reference]} for details. \textcolor{magenta}{[see also section on Regularity for Laplace]}  
\end{remark}
%The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus in order to prove that $\borel_\zeta$ is an algebra homomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.

%Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $\zeta=0$), then 
%\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
%In addition, as proved in \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}, the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
%\[
 %   \series{\psi}\ast\series{\phi}=\int_0^{\zeta}d\zeta' \series{\psi}(\zeta-\zeta')\series{\phi}(\zeta').
%\]
%The convolution product induces an algebra structure on the space $\singexp{\sigma}{\Lambda}(\Omega)$.
%\begin{proof}
%    Let $\tilde{\phi},\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
 %   \begin{align*}
  %      | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
   %     &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
    %    &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
%\end{proof}
%We deduce that also the Laplace transform is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on $H_\theta$.  
%\begin{prop}
 %   Let $\sigma>-1$, $\Lambda>0$ and $\theta\in [0,2\pi)$. Then the Laplace transform $\laplace_{\zeta,0}^\theta$ is $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to $\mathcal{O}(H_\theta)$. 
%\end{prop}
%\begin{proof}
%First of all, from the properties of $\laplace_{\zeta,0}^\theta$ we know that if $\phi, \psi\in\singexp{\sigma}{\Lambda}(\Omega)$, then
%\[\laplace_{\zeta,0}^\theta\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}^\theta\big[{\phi}\big]\laplace_{\zeta,0}^\theta\big[{\psi}\big],\]
%see for instance \cite[Theorem 2.39]{laplace-tfm}. Then we should prove that $\delta$ is a unit: from its definition and the fact that $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we deduce that 
 %   \[
%\laplace_{\zeta,0}^\theta\big[\delta\big]:=\laplace_{\zeta,0}^\theta\big[\borel_\zeta(1)\big]=1.
 %   \]
%Thus, $\delta$ behaves as a Dirac delta distribution acting on $\singexpalg{\sigma}(\Omega)$. Then, if ${\phi}\in\singexp{\sigma}{\Lambda}(\Omega)$
  %   \begin{align*}
%\big[\delta\ast\phi\big](p)&=\int_0^{\zeta(p)} \delta(\zeta(p)-\zeta)\phi(\zeta) \, d\zeta=\phi(p)
 %   \end{align*}
%\end{proof}
\subsubsection{Borel transforms on $1$-Gevrey series}\label{sec:Borel-gevrey}
So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at $\zeta=0$. These formal series are the so-called $1$-Gevrey series:

@@

Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$. Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions. 
Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (assuming they are series of $z$ on the fiber over $\zeta=0$), then following \cite[Definition 5.12]{diverg-resurg-i}, the convolution product $*$ of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is defined as
Furthermore, since $\tilde{\phi}$ and $\tilde{\psi}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is $\hat{\psi}\ast\hat{\phi}$ (see the discussion in Section~\ref{convolution}).   %It's not accidentely that we use the same symbol $*$ that denotes the convolution product to denote the product of two convergent series; indeed, as proved in , %the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
%\[
 %   \hat{\psi}\ast\hat{\phi}=\int_0^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta'),
%\]
%and we refer to \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i} for a proof. 
%\textcolor{orange}{check Lemma 5.14}{where $\hat{\phi}$ and $\hat{\psi}$ are the sum of $\series{\phi}$ and $\series{\psi}$, respectively. }
%\begin{prop}
 %   Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is a $\C$-algebra homomorphism from $1$-Gevrey formal power series $z^{-\tau} \C\llbracket z^{-1} \rrbracket$ to the germs of holomorphic functions $\zeta^{\tau-1} \C\{ z^{-1} \}$.
%\end{prop}
%\begin{proof}
 %   Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ %with $|a_n|\leq A^n n!$ and $A>0$ then  
%\borel_\zeta (z^{-\tau}\tilde{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\frac{1}{\Gamma(\tau)}\int_0^\zeta\sum_{n\geq 0}\frac{a_{n+1}}{n!}(\zeta-\zeta')^{\tau-1}(\zeta')^n\, d\zeta'\\
%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\frac{1}{\Gamma(\tau)}\sum_{n\geq 0} \frac{a_{n+1}}{n!} \int_0^\zeta (\zeta-\zeta')^{\tau-1}(\zeta')^n\, d\zeta'\\
%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\sum_{n\geq 0}a_{n+1} \frac{\zeta^{n+\tau}}{\Gamma(1+n+\tau)}
%where in the third step we use that the Borel transform of $\tilde{\Phi}$ is convergent in a neighbourhood of $\zeta=0$. and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
%which grows as $n(n+1)^{-\tau} A^{n+1}$.
 %   we use $\Gamma(n+1+\tau)\sim \Gamma(n+1) (n+1)^\tau$ as $n\to\infty$. 
%\end{proof}

%
\subsubsection{Action on fractional derivatives and fractional integrals}\label{sec:frac-diff-laplace}
As we'll see in Section~\ref{sec:examples}, it is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
\begin{defn}
    Let $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, b}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, b} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =b}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_b,0}^{-\lambda}$: 
%
\begin{equation*}
    \partial_{\zeta_b,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_b=0}^{p}(\zeta_b(p)-\zeta_b)^{\lambda-1} \varphi(\zeta_b+b)\, d\zeta_b.
\end{equation*}} 
\end{defn}
Notice that the fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\lambda}{\zeta}{b}\,\fracderiv{\mu}{\zeta}{b} & = \fracderiv{\lambda+\mu}{\zeta}{b} \qquad \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).

@@

        The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
